Reconstructing the last known movements of one of Nature's giants

### 2017-06-22 manuscript/blue-whale-ms.tex
Some faffing with figure positioning

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
%\usepackage[round]{natbib} % author-year citations
\usepackage[superscript,biblabel]{cite} % for superscript citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{textcomp} % for parts per mille symbol     
\pagenumbering{arabic}    
\linespread{1.66}

@@

>>>>

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
%\usepackage[round]{natbib} % author-year citations
\usepackage[superscript,biblabel]{cite} % for superscript citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{caption}
\usepackage{subcaption}
\usepackage{textcomp} % for parts per mille symbol     
\pagenumbering{arabic}    
\linespread{1.66}

@@

% 2 panel figure of the two traces - real and simulated

\begin{figure}
  \centering
    \begin{subfigure}{0.8\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1a-raw-dC-dN-data.png}
      \label{fig1a}
    \end{subfigure}

    \begin{subfigure}{0.8\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{fig1b}
    \end{subfigure} 
  \caption{Two panel figure with two traces}
\end{figure}

% two panel with the simulations and map
\begin{figure}
  \centering
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
      \label{fig2a}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{fig2b}
    \end{subfigure} 
  \caption{Two panel figure with trace and map}
\end{figure}

% two panel with the simulations and map
\begin{figure}
  \centering
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
      \label{figa}
    \end{subfigure}

    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{figb}
    \end{subfigure} 
  \caption{Two panel figure with trace and map}
\end{figure}

% two panel with the simulations and map
\begin{figure}
  \centering
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{fig3a}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
      \label{fig3b}
    \end{subfigure} 
  \caption{Two panel figure with trace and map}
\end{figure}

% one panel of the real trace
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1a-raw-dC-dN-data.png}
  \label{fig11a}
  \caption{One panel figure}
\end{figure}

% one panel of the real trace
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
  \label{fig11b}
  \caption{One panel figure}
\end{figure}

% one panel of the real trace
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
  \label{fig11c}
  \caption{One panel figure}
\end{figure}
